*Supplementary Material 2*

### 2022-06-21 ms/si.Rmd
Fix some typos in fossil data

# Format references with pandoc
fossils_table <-
  fossil_ferns_all %>%
  # Filter raw fossil data to just fossils used
  inner_join(
    unique(select(con_fossil_calibration_tips, n_fos)), by = "n_fos") %>%
  verify(nrow(.) == nrow(con_fossil_calibration_tips)) %>%
  # Select columns
  select(
    n_fos, minimum_age, node_calibrated, fossil_taxon, 
    lower = lower_limit_of_oldest_stratigraphic_age,
    upper = upper_limit_of_oldest_stratigraphic_age,
    stratigraphic_age, 
    country, type_locality, formation,
    organs, specimen_holotype, collection,
    reference_raw = reference
  ) %>%
  # Format references
  mutate(reference = cite_pd(
    reference_raw, bib = bib, csl = csl, context = temp_context)) %>%
  select(-reference_raw) %>%
  # Make sure all references in the table have entries in the bibliography
  assert(function(x) str_detect(x, "\\?", negate = TRUE), reference)

>>>>

# Format references with pandoc
fossils_table <-
  fossil_ferns_all %>%
  # Filter raw fossil data to just fossils used
  inner_join(
    unique(select(con_fossil_calibration_tips, n_fos)), by = "n_fos") %>%
  verify(nrow(.) == nrow(con_fossil_calibration_tips)) %>%
  # Select columns
  select(
    n_fos, minimum_age, node_calibrated, fossil_taxon, 
    lower = lower_limit_of_oldest_stratigraphic_age,
    upper = upper_limit_of_oldest_stratigraphic_age,
    stratigraphic_age, 
    country, type_locality, formation,
    organs, specimen_holotype, collection,
    reference_raw = reference
  ) %>%
  # Fix some spelling errors, missing data
  mutate(
    formation = case_when(
      formation == "Dominicam amber deposti" ~ "Dominican amber deposit",
      TRUE ~ formation
    ),
    type_locality =  case_when(
      n_fos == 33 ~ "Burdigalian amber bearing strata of Dominican Republic",
      TRUE ~ type_locality
    )
  ) %>%
  # Format references
  mutate(reference = cite_pd(
    reference_raw, bib = bib, csl = csl, context = temp_context)) %>%
  select(-reference_raw) %>%
  # Make sure all references in the table have entries in the bibliography
  assert(function(x) str_detect(x, "\\?", negate = TRUE), reference)

### 2022-06-21 ms/si2.Rmd
Fix some typos in fossil data

# Tidy fossils in wide format
fossils_long <-
  fossil_ferns_raw %>%
  # Filter to only those actually used in the study
  inner_join(
    n_fos_used, by = "n_fos"
  ) %>%
  verify(all(sort(.$n_fos) == sort(n_fos_used$n_fos))) %>%
  mutate(
    across(everything(), as.character),
    extinct = case_when(
      extinct == "extinct" ~ "^†^",
      extinct == "extant" ~ "",
      TRUE ~ NA_character_
    )) %>%
  assert(not_na, extinct, fossil_taxon) %>%
  # Add fossil taxon header
  mutate(fossil_taxon_header = glue::glue("{fossil_taxon}{extinct}")) %>%
  pivot_longer(names_to = "variable", values_to = "value", -fossil_taxon) %>%
  left_join(
    select(fossil_meta, -description), by = "variable") %>%
  mutate(
    text = as.character(glue::glue("{formatted_name}: {value}"))
  ) %>%
  arrange(fossil_taxon, category, var_order) %>%
  # Drop NA entries
  filter(!is.na(value)) %>%
  filter(variable != "extinct")
```

>>>>

# Tidy fossils in wide format
fossils_long <-
  fossil_ferns_raw %>%
  # Fix some spelling errors, missing data
  mutate(
    formation = case_when(
      formation == "Dominicam amber deposti" ~ "Dominican amber deposit",
      TRUE ~ formation
    ),
    type_locality =  case_when(
      n_fos == 33 ~ "Burdigalian amber bearing strata of Dominican Republic",
      TRUE ~ type_locality
    )
  ) %>%
  # Filter to only those actually used in the study
  inner_join(
    n_fos_used, by = "n_fos"
  ) %>%
  verify(all(sort(.$n_fos) == sort(n_fos_used$n_fos))) %>%
  mutate(
    across(everything(), as.character),
    extinct = case_when(
      extinct == "extinct" ~ "^†^",
      extinct == "extant" ~ "",
      TRUE ~ NA_character_
    )) %>%
  assert(not_na, extinct, fossil_taxon) %>%
  # Add fossil taxon header
  mutate(fossil_taxon_header = glue::glue("{fossil_taxon}{extinct}")) %>%
  pivot_longer(names_to = "variable", values_to = "value", -fossil_taxon) %>%
  left_join(
    select(fossil_meta, -description), by = "variable") %>%
  mutate(
    text = as.character(glue::glue("{formatted_name}: {value}"))
  ) %>%
  arrange(fossil_taxon, category, var_order) %>%
  # Drop NA entries
  filter(!is.na(value)) %>%
  filter(variable != "extinct")
```
